Road Segment Prioritization for Bicycle Infrastructure

### 2020-10-31 README.Rmd
paper: community detection section

Banning cycling flow completely on trunk and primary roads may result in excessively circuitous paths, as seen in Figure \ref{fig:boxplotcircuity}. When routing using the weighting profile in Table **Reference Table**, we see that shortest paths increase by less than 5\% on average from unweighted shortest paths, with the largest increases still below 30\%. When routing on primary and trunk roads is banned, the average increase relative to unweighted shortest paths rises to 10\%, with certain locations experiencing more significant negative effects on accessibility.

@@

>>>>

Banning cycling flow completely on trunk and primary roads may result in excessively circuitous paths, as seen in Figure \@ref(fig:boxplotcircuity). When routing using the weighting profile in Table **Reference Table**, we see that shortest paths increase by less than 5\% on average from unweighted shortest paths, with the largest increases still below 30\%. When routing on primary and trunk roads is banned, the average increase relative to unweighted shortest paths rises to 10\%, with certain locations experiencing more significant negative effects on accessibility.

@@

# Community Detection

One of the main aims of this research is to incorporate egalitarian principles by fairly distributing investments in cycling infrastructure. One way of quantifying this is to split up the city into smaller geospatial areas and target equal investment in each of those areas. Community detection offers us a way to delineate such a split; cyclists are limited in their commuting distance (see Figure \@ref(fig:cyclinghistmanc)), and so trip attractors are more likely to have a local catchment area of cyclists.

```{r cyclinghistmanc, fig.cap="Cycling Commuting Distance - Manchester (2011 Census Data)", out.width="45%", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/histogram_distance_cycling.png")
```

In our case, the network is the city; the nodes are the population-weighted MSOA centroids and the links connecting each MSOA pair are weighted by the potential cycling demand between them. The Louvian method  [@blondel2008fast] is used to separate MSOAs into communities. Potential cycling demand is used since we assume that this is what the cycling demand will be once the cycling infrastructure is added. To assign road links to communities, the following steps are carried out:

1. Create links between MSOA centroids and weigh these links by potential cycling demand between them.
2. Use Louvian method to determine optimal number of communities and assign each MSOA centroid to a community.
3. Assign each road link to the same community as the closest MSOA centroid to it.

The results show that Manchester can be split into three large communities and one small one (Figure \@ref(fig:communitiesmanchester)).

```{r communitiesmanchester, fig.cap="Communities Based on Potential Cycling Demand (Manchester)", out.width="75%", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/communities_alternative_Manchester.png")
```
